Learning to Infer Graphics Programs from Hand-Drawn Images

### 2018-09-23 long.tex
image similarity added to long draft

%% \subsection{Modeling similarity between drawings}
%% Modeling drawings using programs opens up new ways to measure similarity between them.
%% For example, we might say that two drawings are similar if they both contain loops of length 4,
%% or if they share a reflectional symmetry,
%% or if they are both organized according to a grid-like structure.

%% We measure the similarity between two drawings by extracting features
%% of the lowest-cost programs that describe them. Our features are counts of the number of times that different components in the
%% DSL were used (Tbl.~\ref{DSL}).
%% We  then find drawings which are either close together or far apart in program feature space.
%% One could use many
%% alternative similarity metrics between drawings which would capture pixel-level similarities while missing high-level geometric similarities.
%% We used our learned distance metric between trace sets, $L_{\text{learned}}(\cdot|\cdot)$,
%% to find drawings that are either close together or far apart according to the learned
%% distance metric over images.
%% Fig.~\ref{similarityMatrix} illustrates the kinds of drawings that these different metrics put closely together,
%% while Sec.~2 of the supplement shows low dimensional projections of
%% program and image features.

%% \newcommand{\similaritySize}{1cm}
%% \newcommand{\similarityArrowSize}{0.35cm}
%% \begin{figure}[t]
%%   \begin{tabular}{|c|c|}
%%     \multicolumn{1}{c}{\textbf{Close in program space, far in image space}}&
%%     \multicolumn{1}{c}{\textbf{Close in image space, far in program space}}\\\hline&\\

%%     \begin{tabular}{l}
%%       \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-52-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-79-trim.png}\end{minipage}\\\\
%%       \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-16-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-17-trim.png}\end{minipage}
%%     \end{tabular} &

%%     \begin{tabular}{l}
%%       \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-22-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-77-trim.png}\end{minipage}\\\\
%%       \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-64-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-97-trim.png}\end{minipage}
%%     \end{tabular}
%% \\&\\    \hline
%%     %\\
%% %    \multicolumn{1}{c|}{}&&\\\cline{2-3}
%% %    \multicolumn{1}{c|}{}&&\\ \multicolumn{1}{c|}{}
%%     %& %% \begin{tabular}{l}
%%     %%   \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-52-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-79-trim.png}\end{minipage}\\\\
%%     %%   \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-16-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-17-trim.png}\end{minipage}
%%     %% \end{tabular}
%%     %&
%%     %% \begin{tabular}{l}
%%     %%   \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-75-extra-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-89-trim.png}\end{minipage}\\\\
%%     %%   \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-3-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-39-trim.png}\end{minipage}
%%     %% \end{tabular}
%% %\\ \multicolumn{1}{c|}{}&&\\\cline{2-3}\cline{2-3}
%%   \end{tabular}

%%   \centering
%% \caption{Pairs of images either close together or far apart in different features spaces.  The symbol $\leftrightarrow$ points to the compared images. Features of the program capture abstract notions like symmetry and repetition. Distance metric over images is $L_{\text{learned}}(\cdot|\cdot)$ (see Sec.~\ref{generalizingTheHandDrawings}). Similarity of programs captures high-level features like repetition and symmetry, whereas similarity of images corresponds to similar drawing commands being in similar places. See Sec. 2 of the supplement for more examples.}\label{similarityMatrix}  \end{figure}

%% We project these features down to a
%% 2-dimensional subspace using primary component analysis
%% (PCA); see Fig.\ref{NMF}.  One could use many
%% alternative similarity metrics between drawings which would capture pixel-level similarities while missing high-level geometric similarities.
%% We used our learned distance metric between traces, $L_{\text{learned}}(\cdot|\cdot)$, and projected to a 2-dimensional subspace using multidimensional scaling (MDS:~\cite{cox2008multidimensional}). This reveals similarities between the objects in the drawings,
%% while missing similarities at the level of the program.
%% \begin{figure}[h]
%% \centering  \begin{minipage}{\textwidth}\centering
%%   %\includegraphics[width = 0.69\textwidth]{figures/PCA.png}
%%   \includegraphics[width = 0.69\textwidth]{figures/PCA_improved.png}
%%     \caption{PCA on features of the programs that were synthesized for each drawing. Symmetric figures cluster to the right; ``loopy'' figures cluster to the left; complicated programs are at the top and simple programs are at the bottom.}    \label{NMF}
%%   \end{minipage} %\hfill
%%   \begin{minipage}{\textwidth}\centering
%%     \includegraphics[width = 0.69\textwidth]{figures/imageSimilarity.png} 
%%     \caption{MDS on drawings using the learned distance metric, $L_{\text{learned}}(\cdot|\cdot)$. Drawings with similar looking parts in similar locations are clustered together.}
%%   \end{minipage}
%% \end{figure}

\subsection{Extrapolating figures}
Having access to the source code of a graphics program facilitates coherent, high-level image editing.
%For example,
%we could change all of the circles to squares or make all of the lines be dashed.
For example we can extrapolate figures
by increasing the number of times that loops are executed.
Extrapolating repetitive visuals patterns comes naturally to humans,
and is a practical application:
imagine hand drawing a repetitive graphical model structure
and having our system automatically induce and extend the pattern.
Fig.~\ref{extrapolationFigure} shows extrapolations produced by our system.
\begin{figure}[H]\centering
  \includegraphics[width = 0.885\textwidth]{figures/extrapolationMatrix1.png}
  \includegraphics[width = 0.885\textwidth]{figures/extrapolationMatrix2.png}
%  \includegraphics[width = \textwidth]{figures/extrapolationMatrix3.png}  
   \caption{Top, white: hand drawings. Bottom, black: extrapolations produced by our system.}
  \label{extrapolationFigure}
  \end{figure}
%\input{extrapolations.tex}

>>>>

\subsection{Modeling similarity between drawings}
Modeling drawings using programs opens up new ways to measure similarity between them.
For example, we might say that two drawings are similar if they both contain loops of length 4,
or if they share a reflectional symmetry,
or if they are both organized according to a grid-like structure.

We measure the similarity between two drawings by extracting features
of the lowest-cost programs that describe them. Our features are counts of the number of times that different components in the
DSL were used (Tbl.~\ref{DSL}).
We  then find drawings which are either close together or far apart in program feature space.
One could use many
alternative similarity metrics between drawings which would capture pixel-level similarities while missing high-level geometric similarities.
We used our learned distance metric between specs, $L_{\text{learned}}(\cdot|\cdot)$,
to find drawings that are either close together or far apart according to the learned
distance metric over images.
Fig.~\ref{similarityMatrix} illustrates the kinds of drawings that these different metrics put closely together.

\newcommand{\similaritySize}{1cm}
\newcommand{\similarityArrowSize}{0.35cm}
\begin{figure}[t]
  \begin{tabular}{c|c|c|}
    \multicolumn{1}{c}{}    &\multicolumn{1}{c}{\textbf{Close in program space}}&\multicolumn{1}{c}{\textbf{Far apart in program space}}\\\cline{2-3}
    \multicolumn{1}{c|}{}&&\\
    \multicolumn{1}{c|}{    \begin{tabular}{l}\textbf{Close in }\\ \textbf{image space} \end{tabular}}    &
    \begin{tabular}{l}
      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-20-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-21-trim.png}\end{minipage}\\\\
      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-50-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-2-trim.png}\end{minipage}
    \end{tabular} &
    \begin{tabular}{l}
      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-22-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-77-trim.png}\end{minipage}\\\\
      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-64-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-97-trim.png}\end{minipage}
    \end{tabular}\\
    \multicolumn{1}{c|}{}&&\\\cline{2-3}
    \multicolumn{1}{c|}{}&&\\
    \multicolumn{1}{c|}{    \begin{tabular}{c}\textbf{Far apart in }\\ \textbf{image space} \end{tabular}}    &        \begin{tabular}{l}
      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-52-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-79-trim.png}\end{minipage}\\\\
      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-16-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-17-trim.png}\end{minipage}
    \end{tabular}&
    \begin{tabular}{l}
      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-75-extra-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-89-trim.png}\end{minipage}\\\\
      \begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-3-trim.png}\end{minipage}\begin{minipage}{\similarityArrowSize}$\leftrightarrow$\end{minipage}\begin{minipage}{\similaritySize}\includegraphics[width = \similaritySize]{figures/expert-39-trim.png}\end{minipage}
    \end{tabular}
\\    \multicolumn{1}{c|}{}&&\\\cline{2-3}\cline{2-3}    
  \end{tabular}

  \centering
\caption{Pairs of images either close together or far apart in different features spaces.  The symbol $\leftrightarrow$ points to the compared images. Features of the program capture abstract notions like symmetry and repetition. Distance metric over images is $L_{\text{learned}}(\cdot|\cdot)$ (see Section~\ref{generalizingTheHandDrawings}). The off-diagonal entries highlight the difference between these metrics: similarity of programs captures high-level features like repetition and symmetry, whereas similarity of images correspondends to similar drawing commands being in similar places.}\label{similarityMatrix}  \end{figure}

\subsection{Extrapolating figures}
Having access to the source code of a graphics program facilitates coherent, high-level image editing.
%For example,
%we could change all of the circles to squares or make all of the lines be dashed.
For example we can extrapolate figures
by increasing the number of times that loops are executed.
Extrapolating repetitive visuals patterns comes naturally to humans,
and is a practical application:
imagine hand drawing a repetitive graphical model structure
and having our system automatically induce and extend the pattern.
Fig.~\ref{extrapolationFigure} shows extrapolations produced by our system.
\begin{figure}[H]\centering
  \includegraphics[width = 0.885\textwidth]{figures/extrapolationMatrix1.png}
  \includegraphics[width = 0.885\textwidth]{figures/extrapolationMatrix2.png}
  \includegraphics[width = 0.885\textwidth]{figures/extrapolationMatrix3.png}  
   \caption{Top, white: hand drawings. Bottom, black: extrapolations produced by our system.}
  \label{extrapolationFigure}
  \end{figure}
%\input{extrapolations.tex}
